\cvsection{Experience}
\begin{cventries}
  \cventry
    {Lead Software Developer (iOS)}
    {FootLocker/Eastbay}
    {Chicago, Illinois}
    {October 2016 - Current}
    {
      \begin{cvitems}
        \item {Maintenance of Champssports, Footaction, FootLocker, and FootLocker Canada iOS apps. }
        \item {Developing new generation of apps using single codebase in Swift using an MVVM architecture and RxSwift.}
        \item {Set up continuous integration for iOS apps. }
        \item {Implemented code review system based on pull requests. }
        \item {Implemented coding standards used across iOS team. }
      \end{cvitems}
    }
  \cventry
    {Senior Software Developer (iOS)}
    {Isobar (Formerly Roundarchisobar)}
    {Chicago, Illinois}
    {July 2015 - September 2016}
    {
      \begin{cvitems}
        \item {Built SyFy Now, Bravo Now, and USA NOW iOS apps by implementing an iOS cascading sytle system which worked by applying cascading styles to the existing NBC app store app. }
        \item {Developed WellbeingTogether iOS app (WBTogether on the app store) from the ground up using an MVVM architecture and PromiseKit.}
      \end{cvitems}
    }
  \cventry
    {Software Developer (iOS)}
    {Isobar (Formerly Roundarchisobar)}
    {Chicago, Illinois}
    {August 2013 - July 2015}
    {
      \begin{cvitems}
        \item {Developed WellbeingGO iOS app from the ground up using an MVVM architecture. Built app in 5 months with one other developer.}
        \item {Implented Facebook, Google, and Twitter login for McDonalds iOS app. Implemented Arch Card (McDonalds rewards program) 
        management to enable users to add, use, or modify arch cards that they might posess.}
        \item {Implented dashboard view and pin login for Scottrade iOS app and fixed bugs on core iOS application.}
      \end{cvitems}
    }
  \cventry
    {Software Developer Intern}
    {Isobar (Formerly Roundarchisobar)}
    {Chicago, Illinois}
    {June 2013 - August 2013}
    {
      \begin{cvitems}
        \item {Worked on item checkout system for internal use utilizing a Ruby on Rails backend with an iPhone application.}
        \item {Architected iPhone application for use in a client's technical conference.}
        \item {Developed a proof of concept iPad application to improve a user’s multiple screen experience while watching a television show.}
      \end{cvitems}
    }
  \cventry
    {Research Experience Undergraduate}
    {Electronic Visualization Laboratory (University of Illinois at Chicago)}
    {Chicago, Illinois}
    {January 2012 - May 2013}
    {
      \begin{cvitems}
        \item {Designed and developed a web browser and calendar for SAGENext (Scalable Adaptive Graphics Environment) using C++ and Qt.}
        \item {Worked on a SAGENext audio and video chat client for Google Talk.}
      \end{cvitems}
    }
\end{cventries}
